---
title: "06_model"
author: "s222498"
format: html
editor: visual
---

## Modelling of the data

Loading Libraries used for modelling

```{r}
library(tidyverse)
library(broom)
library(dplyr)
library(purrr)
```

Load augmented data generated from 03_augment.qmd and stored in data folder

```{r}
#loading augmentated data for modeling
lm_data <- read_csv("../data/augmented.csv")

```

Modelling using lm() function. Its a linear regression modelling function. In the code below we are performing multiple linear regression.

```{r}
lm_model <- lm(chd ~ tobacco + alcohol+obesity+age, data = lm_data)
```

Making the model data tidy

```{r}
lm_model |> tidy()
```

```{r}
summary(lm_model)
```

Visualizing P value of the model

```{r}
lm_model |> 
  tidy() |> 
  ggplot(aes(x = term,
             y = -log10(p.value))) +
  geom_point() +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed")
```

Including the confidence intervals

```{r}
ci<- lm_model |> 
  tidy(conf.int = TRUE,
       conf.level = 0.95)
ci
```

Visualizing the confidence interval

```{r}
ci |> 
  ggplot(aes(x = estimate,
             y = term,
             xmin = conf.low,
             xmax = conf.high)) +
  geom_errorbarh(height = 0.1) +
  geom_point()
```
